---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_polygons(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
library(tmap)
library(tmaptools)
library(rgdal)
library(sp)
library(osmdata)
s1<-readOGR("/Users/rahul","locations")
#readOGR(dsn,layer). dsn is the location of shape file and layer is the shapefile name without extension. The function reads an OGR data source and layer into a suitable Spatial vector object.
s2<-tmaptools::read_osm(bbox(s1))
#bbox(obj) retrieves spatial bounding box from spatial data
#read_osm() reads Open Street Map data.
tm_shape(s2)+tm_raster()+tm_shape(s1)+tm_dots(col="red",size = 2,shape=16)
#tm_shape() creates a tmap-element that specifies the shape object.
#tm_dots is used to specify the red dots in the map.
```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2
```{r}
library(PBSmapping)
library(ggmap)
s<-importShapefile("/Users/rahul/locations.shp")
#Import an ESRI shapefile (.shp) into either a PolySet or EventData.
n<-as.data.frame(s)
#Convert a compositional object to a dataframe
myLocation<-c(lon=-118.28590256376482, lat=34.02245502729128)
myMap<-get_map(location=myLocation,
source="google", maptype="roadmap",crop=FALSE,zoom=15)
#get_map is a smart wrapper that queries the Google Maps server for a map.
ggmap(myMap)+geom_point(aes(x=X,y=Y),shape=16,color="gold",data=n,size=3)
#Here, we have given the data frame 'n' as the data to be displayed in the layer in geom_point(). Also, specified the shape, size and color of the points to be displayed.
```


